Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-07 tex/main.tex
more
minor

Another interesting fragment is the class of \emph{productive} corecursive
functions. Corecursive functions are functions to a coalgebraic datatype.
These functions can call themselves forever, without their being inconsistent.
Productive corecursive functions are functions that progressively reveal parts
of their (potentially infinite)
output \cite{turner-1995,abbott-et-al-2005,mcbride-productive}.
For example, given a type of infinite streams constructed by $\con{scons}$,
the definition
$\{\forallf{\const{e}} n.\;\, \const{e}(n) \teq \con{scons}(n,\; \const{e}(n + 1))\}$
falls within this fragment, since each call to $\const{e}$ produces one
constructor before entering the nested call. Like terminating recursion,
productive corecursion totally specify the functions it defines. The
following theorem connects these notion with admissibility.

\begin{theorem}
Let
$\DDD = \{ \forallf{\con{f}_1} \vec x.\; \varphi_1, \ldots, \forallf{\con{f}_n} \vec x.\; \varphi_n \}$
be a set of function definitions such that
%
Then the set $\DDD$ is admissible.
\end{theorem}
\begin{proofsketch}
\qed
\end{proofsketch}

>>>>

Another interesting fragment is the class of \emph{productive} corecursive
functions. Corecursive functions are functions to a coalgebraic datatype.
These functions can call themselves forever, without their being inconsistent.
Productive corecursive functions are functions that progressively reveal parts
of their (potentially infinite)
output \cite{turner-1995,mcbride-productive}.
For example, given a type of infinite streams constructed by $\con{scons}$,
the definition
$\{\forallf{\const{e}} n.\;\, \const{e}(n) \teq \con{scons}(n,\; \const{e}(n + 1))\}$
falls within this fragment, since each call to $\const{e}$ produces one
constructor before entering the nested call. Like terminating recursion,
productive corecursion totally specify the functions it defines. The
following theorem connects these notion with admissibility.

\begin{theorem}
Let
$\DDD = \{ \forallf{\con{f}_1} \vec x.\; \varphi_1, \ldots, \forallf{\con{f}_n}
\vec x.\; \varphi_n \}
$ be a set of function definitions such that for all
$(\stypes{\Sigma},\, \sfuns{\Sigma} - \sfundefs{\Sigma})$-interpretations
$\I$, there exists a unique
$\Sigma$-interpretation $\I'$ that extends $\I$
and for which $\I' \models \DDD$.
Then the set\/ $\DDD$ is admissible.
\end{theorem}
\begin{proofsketch}
Let $\varphi$ be a $T$-satisfiable formula closed under function expansion with
respect to $\DDD$.

We must show that formula
$\varphi \wedge (\forallf{\con{f}_1} \vec x.\; \varphi_1) \wedge \cdots \wedge (\forallf{\con{f}_n} \vec x.\; \varphi_n)$ is also $T$-satisfiable.

We have
$\varphi \,\models_T\, \bigwedge\nolimits_{\,i=1}^{n} \{ \varphi_i[ \vec t / \vec x ] \mid \con{f}_i( \vec t ) \in \terms( \varphi ) \}$.

\qed
\end{proofsketch}
